SDR enhancement by clouds

### 2024-03-13 article/article.Rmd
Commit 2024-03-13 18:14

....identification methods from bib....

@@

.....constrains of the site.....

@@

Our monitoring site is operated by the Laboratory of Atmospheric Physics of the Aristotle University of Thessaloniki ()

>>>>

Identification methods from bib

@@

Constrains of the site

@@

Our monitoring site is operating in the Laboratory of Atmospheric Physics of the
Aristotle University of Thessaloniki (\(40^\circ\,38'\,\)N,
\(22^\circ\,57'\,\)E, \(80\,\)m~a.s.l.).
In this study we present data from the period
`r strftime(min(ST_daily$Date), "%d\\ %B %Y")` to
`r strftime(max(ST_daily$Date), "%d\\ %B %Y")`.

The GHI data were measured with a Kipp\ & Zonen CM-21 pyranometer.
During the study period, the pyranometer was independently calibrated three times at
the Meteorologisches Observatorium Lindenberg, DWD, verifying that the stability of
the instrument’s sensitivity was better than $0.7\%$ relative to the initial
calibration by the manufacturer.

For the acquisition of radiometric data, the signal of the pyranometer was sampled
at a rate of $1\,\text{Hz}$.
The mean and the standard deviation of these samples were calculated and recorded
every minute.
The measurements were corrected for the zero offset ("dark signal" in volts), which
was calculated by averaging all measurements recorded for a period of $3\,\text{h}$,
before (morning) or after (evening) the Sun reaches an elevation angle of $-10^\circ$.
The signal was converted to irradiance using a ramped value of the instrument’s
sensitivity between subsequent calibrations.

<!-- Radiation data quality check -->
To  further improve the quality of the irradiance data, a manual screening was
performed to remove inconsistent and erroneous recordings that can occur
stochastically or systematically during the continuous operation of the instruments.
The manual screening was aided by a radiation data quality assurance procedure,
adjusted for the site, which was based on the methods of Long and Shi\ [@Long2006; @Long2008a].
Thus, problematic recordings have been excluded from further processing.
Although it is impossible to detect all false data, the large number of available
data, and the aggregation scheme we used, ensures the quality of the radiation
measurements used in this study.

<!-- Data selection -->
Due to the significant measurement uncertainty when the Sun is near the horizon, we
have excluded all measurements with solar zenith angle (SZA) greater than $`r 90-MIN_ELEVA`^\circ$.
Moreover, due to obstructions around the site (hills and buildings) that block the direct irradiance, we excluded data with azimuth angle in the range
$`r FIBais_Az_1`^{\circ}$--$`r FIBais_Az_2`^{\circ}$ and with SZA greater than $`r 90 - FIBais_Elev`^{\circ}$.
